---
title: "Model calibration"
author: "Teresa Ortiz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>", 
    cache = TRUE
)
```

To install the package use [devtools](https://github.com/r-lib/devtools) 
(devtools is available on CRAN).

```{r, message=FALSE}
# devtools::install_github("tereom/quickcountmx")
library(quickcountmx)
library(tidyverse)
```

The package includes the results of the 2012 Guanajuato Governor election, which
will be used to exemplify the functions.

```{r}
library(dplyr)
data("gto_2012")
dplyr::glimpse(gto_2012)
```

The variables are described in the package documentation `?gto_2012`.

## Examples: bayesian estimation

### Calibration for one model (vote count)


```{r}
counts <- mrp_party_estimation(gto_2012, party = pan_na, 
  stratum = distrito_loc_17, frac = 0.04, 
  seed = 211871, n_chains = 2, n_burnin = 500, n_iter = 1000, model_string = "model_bern_t")
qplot(counts$n_votes, binwidth = 1000) + 
  geom_vline(xintercept = sum(gto_2012$pan_na), colour ='red')
```

```{r}
R2jags::traceplot(counts$fit, varname = 'deviance')
```

Calibration run for one party (pan):

```{r}
gto_pan <- calibration_party(gto_2012, party = pan_na, frac = 0.075,
        stratum = distrito_loc_17, n_iter = 1500, n_burnin = 500, 
        cl_cores = 5, n_chains = 1, seed = 19112, n_rep = 3)
pan <- summary_calibration_party(gto_pan)
```

```{r}
pan$plot
pan$coverage
```

Calibration run for one party (prd):


```{r}
gto_prd <- calibration_party(gto_2012, party = prd, frac = 0.075,
        stratum = distrito_loc_17, n_iter = 1500, n_burnin = 500, 
        cl_cores = 5, n_chains = 1, seed = 19112, n_rep = 3)
prd <- summary_calibration_party(gto_prd)
```

```{r}
prd$plot
prd$coverage
```

## Calibration: bayesian estimation


## Calibration for vote proportion model

```{r, propcalib}
calibration_gto <- calibration_prop(gto_2012, pri_pvem:otros, frac = 0.075, 
        stratum = distrito_loc_17, n_iter = 1500, n_burnin = 500, 
        n_chains = 1, seed = 191127, cl_cores = 1, n_rep = 3, 
        model_string = "model_bern_t")
```


```{r a}
calib_summary <- summary_calibration(calibration_gto)
calib_summary
```



### Coverage report for vote proportions with missing strata



```{r, propcalib2}
calibration_gto_miss <- calibration_prop(gto_2012, pri_pvem:otros,
        frac = 0.075, stratum = distrito_loc_17, 
        n_iter = 1500, n_burnin = 500, 
        n_chains = 1, seed = 19331, cl_cores = 1, n_rep = 10, 
        model_string = "model_bern_t", num_missing_strata = 2)
```

```{r b}
calib_summary <- summary_calibration(calibration_gto_miss)
calib_summary
```

## Calibration: Ratio estimation

### Coverage report for vote proportions  (ratio estimator)


```{r calibrat}
set.seed(1211)
gto_stratum_sizes <- gto_2012 %>%
  dplyr::group_by(distrito_loc_17) %>%
  dplyr::mutate(n_stratum = n())

calib_ratio <- parallel::mclapply(1:200, function(i) {
  gto_sample <- select_sample_prop(gto_stratum_sizes, stratum = distrito_loc_17, 
                                   0.075)
  ratio <- ratio_estimation(gto_sample, stratum = distrito_loc_17, 
                            n_stratum = n_stratum, ... = pri_pvem:otros)
  ratio <- ratio %>% mutate(n_sim = i)
  ratio 
}, mc.cores = 4) %>% bind_rows
```

```{r sumcalib}
gto_gather <- gto_2012 %>% dplyr::select(casilla_id, pri_pvem:otros) %>%
  tidyr::gather(party, votes, pri_pvem:otros)
actual <- gto_gather %>% group_by(party) %>% 
  summarise(n_votes = sum(votes, na.rm = T)) %>%
  mutate(prop_votes = 100*n_votes/sum(n_votes, na.rm=T))
calib_ratio <- calib_ratio %>% left_join(actual) %>% ungroup() %>%
  mutate(coverage = r - 2*std_error < prop_votes & r + 2*std_error > prop_votes,
         precision = 2 * std_error)
```



```{r plotcalib}
ggplot(filter(calib_ratio, n_sim <= 200), aes(x = n_sim, y = r, ymin = r - 2*std_error,
       ymax = r + 2*std_error )) + geom_linerange(colour='red') +
  geom_hline(data = actual, aes(yintercept = prop_votes)) + 
  facet_wrap(~party, scales="free_y")
```

```{r ax}
calib_summary <- calib_ratio %>% group_by(party) %>% summarise(coverage = mean(coverage), 
          precision_media = mean(precision), n_sims = n())
calib_summary
```

### Coverage report for vote proportions with missing strata (ratio estimator)

Randomly collapsing to observed strata


```{r calibrat2}
set.seed(1211)
gto_stratum_sizes <- gto_2012 %>%
  dplyr::group_by(distrito_loc_17) %>%
  dplyr::mutate(n_stratum = n())

calib_ratio_miss <- parallel::mclapply(1:200, function(i) {
  # select sample
  gto_sample <- select_sample_prop(gto_stratum_sizes, 
                  stratum = distrito_loc_17, 0.075) %>%
                mutate(distrito_coll = distrito_loc_17) %>%
                select(-n_stratum)
  strata <- unique(gto_2012$distrito_loc_17)
  missing <- sample(strata, 3)
  present <- setdiff(strata, missing)
  gto_sample_miss <- gto_sample %>% filter(distrito_loc_17 %in% present)
  collapse_to <- sample(present, length(missing))
  new_strata <- data_frame(distrito_loc_17 = c(missing, present), 
             distrito_coll = c(collapse_to, present)) 
  gto_2012_collapsed <- left_join(gto_2012, new_strata, 
                                  by = "distrito_loc_17") 
  gto_sample_miss <- gto_sample_miss %>%
    left_join(gto_2012_collapsed %>% group_by(distrito_coll) %>%
      summarise(n_stratum = n()), by ="distrito_coll")
  ratio <- ratio_estimation(gto_sample_miss, stratum = distrito_coll, 
                            n_stratum = n_stratum, ... = pri_pvem:otros)
  ratio <- ratio %>% mutate(n_sim = i)
  ratio 
  }, mc.cores = 4) %>% bind_rows
```

```{r sumcalib2}
gto_gather <- gto_2012 %>% dplyr::select(casilla_id, pri_pvem:otros) %>%
  tidyr::gather(party, votes, pri_pvem:otros)
actual <- gto_gather %>% group_by(party) %>% 
  summarise(n_votes = sum(votes, na.rm = T)) %>%
  mutate(prop_votes = 100*n_votes/sum(n_votes, na.rm=T))
calib_ratio_miss <- calib_ratio_miss %>% left_join(actual) %>% ungroup() %>%
  mutate(coverage = r - 2*std_error < prop_votes & r + 2*std_error > prop_votes,
         precision = 2 * std_error)
```



```{r plotcalib2}
ggplot(filter(calib_ratio_miss, n_sim <= 200), aes(x = n_sim, y = r, ymin = r - 2*std_error,
       ymax = r + 2*std_error )) + geom_linerange(colour='red') +
  geom_hline(data = actual, aes(yintercept = prop_votes)) + 
  facet_wrap(~party, scales="free_y")
```


```{r ax2}
calib_summary <- calib_ratio_miss %>% group_by(party) %>% summarise(coverage = mean(coverage), 
          precision_media = mean(precision), n_sims = n())
calib_summary
```


## Reporting unique intervals

```{r}
calib_ratio <- calib_ratio %>% mutate(int_l = r - 2*std_error,
                                      int_r = r + 2*std_error)
calibration_gto <- calibration_gto %>% 
  mutate(coverage = prop_votes < int_r & prop_votes > int_l)

```

```{r}
ratio <- select(calib_ratio, n_sim, party, int_l, int_r)  %>% 
  mutate(method = 'ratio')
bayesian <- select(calibration_gto, n_sim, party, int_l, int_r) %>% mutate(method = 'bayesian')
intervals <- bind_rows(ratio, bayesian) 
```

```{r}
# also try with median and mean instad of min/max
intervals_max <- intervals %>% group_by(n_sim, party) %>%
  mutate(int_l = min(int_l), int_r = max(int_r)) %>% left_join(actual)
```

```{r}
intervals_max %>% 
  ungroup %>%
  mutate(coverage = int_l < prop_votes & int_r > prop_votes) %>%
  group_by(party, method) %>%
  mutate(n = max(n_sim)) %>%
  filter(n_sim < min(n)) %>%
  group_by(party) %>%
  summarise(coverage = mean(coverage))
  
```