---
title: "Model calibration"
author: "Teresa Ortiz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>", 
    cache = TRUE
)
```

To install the package use [devtools](https://github.com/r-lib/devtools) 
(devtools is available on CRAN).

```{r, message=FALSE}
# devtools::install_github("tereom/quickcountmx")
library(quickcountmx)
library(tidyverse)
```

The package includes the results of the 2012 Guanajuato Governor election, which
will be used to exemplify the functions.

```{r}
data("gto_2012")
glimpse(gto_2012)
```

The variables are described in the package documentation `?gto_2012`.



## Calibration for one model (vote count)

Posterior predictive check for one run:

```{r}
counts <- mrp_party_estimation(gto_2012, party = pan_na, 
  stratum = distrito_loc_17, frac = 0.04, 
  seed = 211871, n_chains = 2, n_burnin = 500, n_iter = 1000)
qplot(counts$n_votes, binwidth = 1000) + 
  geom_vline(xintercept = sum(gto_2012$pan_na), colour ='red')
```

Calibration run for one party (pan):

```{r}
out <- calibration_party(gto_2012, party = pan_na, frac = 0.02,
        stratum = distrito_loc_17, n_iter = 1000, n_burnin = 500, 
        cl_cores = 3, n_chains = 2, seed = 19112, n_rep = 10)
alpha_r <- 1 - 0.95
cal_summary <- out %>% group_by(n_sim) %>%
  summarise(mean_post = mean(n_votes), inf = quantile(n_votes, alpha_r / 2), 
            sup = quantile(n_votes, 1 - alpha_r/2), actual_votes = actual_votes[1])
ggplot(cal_summary, aes(x = factor(n_sim), y = mean_post, ymin = inf, ymax = sup)) + 
  geom_hline(aes(yintercept = actual_votes[1]), colour = 'red') +
  geom_point() + geom_linerange()
## Coverage 
cal_summary %>% summarise(coverage = mean(inf < actual_votes & sup > actual_votes))
```

Calibration run for one party (pan):


```{r}
out <- calibration_party(gto_2012, party = prd, frac = 0.02,
        stratum = distrito_loc_17, n_iter = 1000, n_burnin = 500,
        cl_cores = 3, n_chains = 2, seed = 19112, n_rep = 10)
alpha_r <- 1 - 0.95
cal_summary <- out %>% group_by(n_sim) %>%
  summarise(mean_post = mean(n_votes), inf = quantile(n_votes, alpha_r / 2), 
            sup = quantile(n_votes, 1 - alpha_r/2), actual_votes = actual_votes[1])
ggplot(cal_summary, aes(x = factor(n_sim), y = mean_post, ymin = inf, ymax = sup)) + 
  geom_hline(aes(yintercept = actual_votes[1]), colour = 'red') +
  geom_point() + geom_linerange()
## Coverage 
cal_summary %>% summarise(coverage = mean(inf < actual_votes & sup > actual_votes))
```



