---
title: "Model calibration"
author: "Teresa Ortiz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>", 
    cache = TRUE
)
```

To install the package use [devtools](https://github.com/r-lib/devtools) 
(devtools is available on CRAN).

```{r, message=FALSE}
# devtools::install_github("tereom/quickcountmx")
library(quickcountmx)
```

The package includes the results of the 2012 Guanajuato Governor election, which
will be used to exemplify the functions.

```{r}
library(dplyr)
data("gto_2012")
dplyr::glimpse(gto_2012)
```

The variables are described in the package documentation `?gto_2012`.



## Calibration for one model (vote count)

Posterior predictive check for one run:

```{r}
counts <- mrp_party_estimation(gto_2012, party = pan_na, 
  stratum = distrito_loc_17, frac = 0.04, 
  seed = 211871, n_chains = 2, n_burnin = 500, n_iter = 1000, model_string = "model_bern_t")
qplot(counts$n_votes, binwidth = 1000) + 
  geom_vline(xintercept = sum(gto_2012$pan_na), colour ='red')
```

Calibration run for one party (pan):

```{r, pancalib}
out <- calibration_party(gto_2012, party = pan_na, frac = 0.02,
        stratum = distrito_loc_17, n_iter = 1000, n_burnin = 500, 
        cl_cores = 3, n_chains = 2, seed = 19112, n_rep = 10)
alpha_r <- 1 - 0.95
cal_summary <- out %>% group_by(n_sim) %>%
  summarise(mean_post = mean(n_votes), inf = quantile(n_votes, alpha_r / 2), 
            sup = quantile(n_votes, 1 - alpha_r/2), actual_votes = actual_votes[1])
ggplot(cal_summary, aes(x = factor(n_sim), y = mean_post, ymin = inf, ymax = sup)) + 
  geom_hline(aes(yintercept = actual_votes[1]), colour = 'red') +
  geom_point() + geom_linerange()
## Coverage 
cal_summary %>% summarise(coverage = mean(inf < actual_votes & sup > actual_votes))
```

Calibration run for one party (pan):


```{r, prdcalib}
out <- calibration_party(gto_2012, party = prd, frac = 0.05,
        stratum = distrito_loc_17, n_iter = 1000, n_burnin = 500,
        cl_cores = 3, n_chains = 2, seed = 19112, n_rep = 10)
alpha_r <- 1 - 0.95
cal_summary <- out %>% group_by(n_sim) %>%
  summarise(mean_post = mean(n_votes), inf = quantile(n_votes, alpha_r / 2), 
            sup = quantile(n_votes, 1 - alpha_r/2), actual_votes = actual_votes[1])
ggplot(cal_summary, aes(x = factor(n_sim), y = mean_post, ymin = inf, ymax = sup)) + 
  geom_hline(aes(yintercept = actual_votes[1]), colour = 'red') +
  geom_point() + geom_linerange()
## Coverage 
cal_summary %>% summarise(coverage = mean(inf < actual_votes & sup > actual_votes))
```

## Calibration for vote proportion model

```{r, propcalib}
calibration_gto <- calibration_prop(gto_2012, pri_pvem:otros, frac = 0.02, 
        stratum = distrito_loc_17, n_iter = 1500, n_burnin = 500, 
        n_chains = 2, seed = 1911275, cl_cores = 2, n_rep = 2, model_string = "model_t")
```



```{r}
head(calibration_gto)
calibration_summary <- calibration_gto %>% 
  mutate(covered = ((mean_post - 1.96 * std_dev_post) < prop_votes & (mean_post + 1.96 * std_dev_post) > prop_votes)*1) %>% 
  group_by(party) %>% summarise(coverage = mean(covered), n_sims = length(covered))
calibration_summary
```


```{r}
means_party <- calibration_gto %>% group_by(party) %>% 
  summarise(mean_party = mean(mean_post), prop_votes = mean(prop_votes),
            `2_ee` = 1.96*mean(std_dev_post))
arrange(means_party, prop_votes) %>% mutate(dif = mean_party - prop_votes)
ggplot(calibration_gto, aes(x = n_sim, ymin = mean_post - 1.96 * std_dev_post,
                            ymax = mean_post + 1.96 * std_dev_post)) +
  geom_linerange(colour='red') + 
  facet_wrap(~party, scales = 'free_y') +
  geom_hline(data = means_party, aes(yintercept = mean_party), colour ='red') +
  geom_hline(data = means_party, aes(yintercept = prop_votes), colour ='black') 
```

Número de votos

```{r, numvotecalib}
num_party <- calibration_gto %>% group_by(party) %>% 
  summarise(mean_party = mean(mean_post), prop_votes = mean(prop_votes),
            `2_ee` = 1.96*mean(std_dev_post))
arrange(means_party, prop_votes) %>% mutate(dif = mean_party - prop_votes)
ggplot(calibration_gto, aes(x = n_sim, ymin = mean_post - 1.96 * std_dev_post,
                            ymax = mean_post + 1.96 * std_dev_post)) +
  geom_linerange(colour='red') + 
  facet_wrap(~party, scales = 'free_y') +
  geom_hline(data = means_party, aes(yintercept = mean_party), colour ='red') +
  geom_hline(data = means_party, aes(yintercept = prop_votes), colour ='black')
```

