---
title: "Sampling and estimation methods"
author: "Teresa Ortiz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>", 
    cache = TRUE
)
```

To install the package use [devtools](https://github.com/r-lib/devtools) 
(devtools is available on CRAN).

```{r, message=FALSE}
# devtools::install_github("tereom/quickcountmx")
library(quickcountmx)
library(tidyverse)
```

The package includes the results of the 2012 Guanajuato Governor election, which
will be used to exemplify the functions.

```{r}
data("gto_2012")
glimpse(gto_2012)
```

The variables are described in the package documentation `?gto_2012`.

### Random sampling

The functions `select_sample_str` and `select_sample_prop` allow for simple 
random sampling and stratified random sampling. For example to 
select a simple random sample with 2% of the data:

```{r}
gto_srs <- select_sample_prop(gto_2012, frac = 0.02)
```

For stratified sample we can specify the desired sample size in each stratum 
or we can specify the percentage of the observations to be selected within 
each stratum (allocation corresponding to probability proportional to size).

If we are to specify sample size within strata we need to supply a data.frame
with the sample sizes. For example, lets suppose we are stratifying by federal 
district and the data.frame `allo_df` specifies the allocation in each stratum, 
in this case we want to sample 3 polling stations in each stratum:

```{r}
allo_df <- data.frame(distrito_fed_17 = 1:20, n = rep(3, 20))
allo_df
```
We use the function `select_sample_str`:
```{r}
gto_equal <- select_sample_str(gto_2012, allo_df, n, distrito_fed_17)
table(gto_equal$distrito_fed_17)
```

And selecting with probability proportional to size (pps) we can choose a 
stratified sample with 2% of the polling stations:

```{r}
gto_str <- select_sample_prop(gto_2012, distrito_fed_17, 0.02, seed = 281982)
table(gto_str$distrito_fed_17)
```
Note that there is a parameter `seed` so we can replicate a sample.

### Estimation

We begin exemplifying ratio estimation, to compute estimations using ratio
estimator we need to know the size of each strata (in this case strata are the 
local districts):

```{r}
# count number of polling stations per stratum
gto_stratum_sizes <- gto_2012 %>%
    dplyr::group_by(distrito_loc_17) %>%
    dplyr::mutate(n_stratum = n())
```

Now lets suppose we have a stratified random sample with 4% of the data (pps):

```{r}
gto_sample <- select_sample_prop(gto_stratum_sizes, stratum = distrito_loc_17, 
    0.06, seed = 19291)
```

We then call the function `ratio_estimation()`

```{r}
ratio_estimation(gto_sample, stratum = distrito_loc_17, n_stratum = n_stratum, 
    ... = pri_pvem:otros)
```
For Mr. P, we fit a model per candidate and then compute the proportions using
the simulated counts for each polling station-candidate. The following 
function selects a sample of 6% percent of the data, fits the model using the 
sample and predicts for the population. Alternatively, one can select a sample
before calling the function, and use the parameter `frac_sample=1`, however, 
for the estimation to take place the `data` must include all polling stations 
and NA whenever the polling station was not in the sample.

```{r, message=FALSE}
mrp_gto <- mrp_estimation(gto_2012, pri_pvem:otros, frac = 0.06, 
    stratum = distrito_loc_17, n_iter = 200, n_burnin = 100, 
    n_chains = 2, seed = 19291, parallel = TRUE, mc_cores = 8)
```

`mrp_estimation` returns a list with the fitted models, so we can evaluate
examine the model and evaluate convergence:

```{r, fig.width=8, fig.height=12}
mrp_gto$jags_fits$pri_pvem$model
plot(mrp_gto$jags_fits$pan_na)
```

It also includes a summary table with posterior estimations:

```{r}
mrp_gto$post_summary
```



